---
title: "Homework Five"
author: "Noah Kreski"
date: "November 3, 2018"
output: github_document
---
###Problem One
```{r setup, include = FALSE}
library(tidyverse)
```

```{r Problem One, message = FALSE}

#I am creating a dataframe of tidy longitudinal data
df = tibble(
  #I am beginning by getting all file names using list.files
  filenames = list.files("./data/Longitudinal/", full.names = T),
  #I am using the map function to iterate over files and save the result as a new variable
  map(filenames,read_csv))%>%
  #In order to further tidy the data, I am unnesting
 unnest()%>%
  #I'm gathering the data values to tidy them
 gather(key = week, value = value, week_1:week_8)%>%
  #I am mutating file names to just have arm and ID
 mutate(week = as.numeric(str_replace(week, "week_","")))%>%
 mutate(filenames = str_replace(filenames, "./data/Longitudinal/", ""))%>%
 mutate(filenames = str_replace(filenames, ".csv", ""))%>%
 mutate(filenames = str_replace(filenames, "con", "Control"))%>%
 mutate(filenames = str_replace(filenames, "exp", "Experimental"))%>%
  #I am creating a copy of the filename to split into ID and Arm variables
 mutate(filenames_split = filenames)%>%
 separate(filenames_split, into = c("arm", "subject_id"), sep = "_")%>%
 mutate(arm = as.factor(arm))%>%
 mutate(subject_id=as.numeric(subject_id))
#I want to show the final data frame
df
```

This data frame contains the relevant longitudinal data tidied, so each row is a value for a given arm, subject, and week, with the associated file.

```{r plot longitudinal}
#I am plotting data over time by participant, grouped by arm
ggplot(data = df, aes(x=week, y = value, group = filenames , color = arm))+ geom_line() + labs(title = "Data Values over Time by Arm" )
       
```

The above visual shows the patterns in data over time by participant, grouped by arm. The experimental arm showed much more growth over time, whereas the control group values stagnated.

###Problem Two

The raw data provide homicide victim information, such as name and demographics of sex and race, but also geographic information, both by city and state as well as latitude and longitude. The outcome of each homicide, given by the variable "disposition" provides context for whether a homicide is solved or unsolved in these 50 geographic areas.

```{r Problem Two, message = FALSE}
#I am reading in the homicide data, and creating the city_state variable, while also removing an erroneous entry.
Washington_data = read_csv("./data/WashingtonPost/homicide-data.csv")%>%
                  mutate(city_state = paste(city,state, sep = ","))%>%
                  filter(city_state != "Tulsa,AL")
#This gets the total number of homicides.                  
Washington_Summary = Washington_data%>%
                     group_by(city_state)%>%
                     summarize(n = n())
#This gets the unsolved homicides by location.
Washington_unsolved = Washington_data%>%
                      filter(disposition != "Closed by arrest")%>%
                      group_by(city_state)%>%
                      summarize(unsolved_n = n())
#I am combining the values into a single table.
Washington_total = full_join(Washington_Summary, Washington_unsolved, by = "city_state")

```

The above data frame gets the total and unsolved homicides by city into one convenient place.

```{r Problem Two Baltimore, message = FALSE}
#I am getting the proportion of homicides that are unsolved in Baltimore, and tidying to get the estimate and confidence interval.
prop.test(filter(Washington_total, city_state == "Baltimore,MD")$unsolved_n, filter(Washington_total, city_state == "Baltimore,MD")$n)%>%
  broom::tidy()%>%
  select(estimate, conf.low, conf.high)
```

These data provide the proportion of homicides that are unsolved in Baltimore, with a confidence interval.

```{r problem two pipeline}
#I am creating a function to read in a city and produce a proportion with CI.
proportion_function = function(x) {
  
  prop.test(filter(Washington_total, city_state == x)$unsolved_n, filter(Washington_total, city_state == x)$n)%>%
  broom::tidy()%>%
  select(estimate, conf.low, conf.high)
}
#This code will iterate the function over all cities, produce a column with tibbles, and unnest to generate proportions and CIs for every city.
city_df = tibble(city_list = (c(Washington_total$city_state)),
map(city_list, proportion_function)) %>%
unnest()
```

The above code produces a tidy data frame with the proportion of unsolved homocides for each city, and a confidence interval.

```{r problem two visualization}
#I am ordering the above data by proportion.
city_df%>%
mutate(city_list = forcats::fct_reorder(city_list, estimate))%>%
#I am creating a visual with proportions by location, with error bars, and formatting appropriately.
ggplot( aes(x = city_list, y = estimate, group = city_list)) + geom_point() +theme(axis.text.x = element_text(angle = 70, hjust = 1)) + geom_errorbar( mapping=aes(x=city_list, ymin=conf.low, ymax=conf.high))+labs(title = "Proportion of Homicides that are Unsolved by Location", x = "Location", y = "Proportion of homicides that are Unsolved")
```

The above visualization showcases the proportion of homicides that are unsolved by city.